\biohead{Elizabeth Annie Ames}{}

Elizabeth Annie Ames was born in (about) 1731.  She married John Hill in 1751 and they had ten children (see\p{John_Hill}).

She died aged 75 on 6 July 1806 in Paulton, Somerset, and was buried in Paulton Churchyard on 10 July (see\p{John_Hill} for the inscription on her tombstone).

Her will read:

\begin{quotation}
Considering the certainty of death and the uncertainty of the time thereof I, Elizabeth Hill, of Paulton in the County of Somerset, widow do make my last will and testament. I give and bequeath unto my son Simon Hill one silver tankard, one pair of silver salts, two sile pepper boxes and all my chinaware also I give and bequeath unto my said son Simon Hill the bedstead and bed furniture together with the several chairs tables and drawers with all other furniture which is kept in the room commonly called the best room in the house in which I at present reside to be made use of by him for the term of his natural life and from and immediately after his decease I give and bequeath the same and every part thereof and also one round mahogany table, half a dozen leather bottomed chairs and one small bed, bedstead and furniture now being in the room commonly called the little room unto my granddaughter Elizabeth Hill Broddribb to and for her own proper use and benefit. I give and bequeath to my son George Hill the bed with chintz hangings together with the bedstead and furniture thereunto being in the room which I usually sleep also my clock, one large mahogany table and one mahogany chest of drawers. I give and bequeath to my son Robert Hill the bed with purple hangings together with the bedstead and furniture thereunto belonging situate standing and being the said last mentioned room. Also my next largest mahogany table half a dozen chairs painted green and one mahogany chest of drawers. I give and bequeath unto my daughter Susannah James widow all my wearing apparel of every sort and kind and also all my rings and bequeath all my table linen bedlinen and bedclothes (except such as is herein before bequeathed) unto and amongst my several children, Simon Hill, Thomas Hill, Susannah James, George Hill and Robert Hill and my said granddaughter Elizabeth Hill Broddribb equally to be divided between them and share alike. I give and bequeath all such rights, shares and interests that I may be entitled to at the time of my decease of and in any Coalworks in the County of Somerset and particularly in certain coalworks now carrying on in the Parishes of Paulton and Radstock in the said County together with the several privileges profits present and future advantages emoluments hereditaments and apprentices. The mark of Elizabeth Hill, Robert Langford and Benjamin Hill, witnesses. Such right shares and my grandchildren Caleb Parsons, Maria Parsons, William Parsons, Elizabeth Parsons and Thomas everything remaining to be divided.
\end{quotation}

(This will was written before George Hill's children were born. The original document is held by a living family member.)
