\biohead{Eric Geoffrey West Hancox}{Eric_Geoffrey_West_Hancox}{Geoffrey in the 1930s.\cite{}}

Eric Geoffrey West Hancox (or `Geoffrey' to his family) was  born on July/August 1911 in Rock Ferry to Richard James Hancox (1873--1970) and Marian Gilmour Hancox nee Croskery (1879--1970) [Ericgeoffbirth] and christened on 10 September [Ericgeoff christen].  He had one sister, Joan Nyria Hancox (1918--2004).  

Geoffrey became a geologist, doing his undergraduate studies at the University of Liverpool and the Imperial College of Science London University, before moving to Canada and the US in the 30s to gain his PhD.

He arrived in New York on the ''Scythia'' on 11 September 1934; he was listed on the ships manifest as a student.\cite{NYpassengers}
The following year he went into the US from Canada, to Babb, Montana, and is listed as a student at both the University of California
and the University of Arizona in Tuscon\cite{USCanadaBorderCrossings} where he was a Commonwealth Fund scholar
(now the `Harkness Fellowship'; at the time this was akin to a Rhodes Scholarship, and was awarded to foreign students studying in the US).

The following is an article from the front page of the \emph{Casa Grande Dispatch} newspaper of Tucson, Arizona on 25 May 1934.\cite{CasaP1}

\begin{quotation}
\textbf{Recognition Given U Of A By British}

TUCSON May 18

International recognition of the strength of the department of geology at the University of Arizona and of the wealth of field research opportunity in the state has come through the announcement that a Commonwealth Fund Fellowship has been awarded to an English student for specific graduate study at the University of Arizona. President Homer LeRoy Shants of the University indicated today that the selection of the University of Arizona for one of these school places its department on an equal plane with the great centers of study in that field. The fellowship has been awarded to Eric Geoffrey Hancox, a graduate of the University of Liverpool and of the Imperial College of Science, London University.
\end{quotation}

In 1935 Geoffrey was living at 910 East Helen Street in Tucson.\cite{USCities}
He then obtained work as a mining geologist in  the Mawchi tungsten mines, in Burma, but was killed in a mining accident on 10 August 1937.
Probate announcement:\cite{EGWHprobate}
\begin{quotation}
Probate: Hancox Eric Geoffrey of Morant, Herbert Road, New Milton, Hampshire died 10 August 1937 at Mawchi Mines Burma India. Administration Winchester 26 November to Richard James Hancox retired bank inspector. Effects \pounds734 19 s 9 d.
\end{quotation}
