\biohead{James Denton Barker}{}

James was born on the 18th July 1876 at 10 Falkner Street, Toxteth, Liverpool \cite{JamesDBarkerBirth}. His parents were  Thomas Henry Barker (\p{Thomas_Henry_Barker}) and Mary Ellen Moulsdale (\p{Mary_Ellen_Moulsdale}). He was the eldest of seven and his siblings were Charles Frederick Strangways Barker (\p{Charles_Frederick_Strangways_Barker}),  Reverend Thomas Percy Conyers Barker (\p{Thomas_Percy_Conyers_Barker}), Francis Darcy Mead Barker (\p{Francis_Darcy_Mead_Barker}), William Danby Holt Barker (\p{William_Danby_Holt_Barker}), Jonathan Tong Barker (\p{Jonathan_Tong_Barker}), and Henry Bertram Mitford Barker (\p{Henry_Bertram_Mitford_Barker}).  

In 1881 (aged four), he was living at 44 Orell Park with his father, mother, his younger brothers (Charles, Thomas, and Francis), and two great-aunts, Mary Denton (age 72) and Isabella Hazlewood (age 72).\cite{UKCensusRG11_3688}

He was educated at Warwreck College, Aintree, Liverpool.

He married Kathleen Munday on 4th April 1914 at the Wandsworth Registry Office \cite{JamesDBarkerMarriage} and they had three children: Bertram Mead Denton Barker (\p{Bertram_Mead_Denton_Barker}), Ralph Munday Denton-Barker (\p{Ralph_Munday_Denton_Barker}) and Virginia Kathleen Denton Barker (\p{Virginia_Kathleen_Denton_Barker})  and they lived at 26 Devonshire Road, Birkenhead, Cheshire.

He worked as an average adjuster for nearly 50 years with Messrs. Henry M.Loftus and Son and retired in 1950. In 1925 he was the Chairman of the Association of Average Adjusters (and presided over the annual dinner at the Princes Hotel, Piccadilly on 8 May 1925.)

James died on 30 September 1958, at 23 Lemsford Road, St Albans, Hertfordshire \cite{JamesDBarkerDeath} although they were living at 47 West Way, Harpenden at the time. The Probate notice read:
"" Barker James Denton of 47 West Way Harpenden Hertfordshire died 30 September 1958 at 23 Lemsford Road St Albans Hertfordshire Probate London 22 January to Ronald George Taylor and Douglas James Walker solicitors Effects £7011 8s. 3d.  ""




