\biohead{Joan Nyria Hancox}{Late 1950s in Great Witley.\cite{FlickrNyria}}

Joan Nyria Hancox (always known as Nyria) was born on 23 February 1918 in Bebington, Cheshire\cite{BMDIndex_JoanNyriaHancox_birth} and was the only daughter of Richard James Hancox (\p{Richard_James_Hancox})  and Marian Gilmour Croskery (\p{Marian_Gilmour_Croskery}).\cite{NyriaBirth} She was christened on 7 April 1918.\cite{NyriaChristening} She had one older brother, Eric Geoffrey West Hancox (\p{Eric_Geoffrey_West_Hancox}).  They lived at 8 Thorburn Road, Rock Ferry, Birkenhead, Cheshire. 

From the age of 6, she attended Howell's School, Denbigh as a boarder (in \idx{Wales}).\cite{OralHistoryJDB2008}

In the mid-thirties she studied nursing at Guy's Hospital (enrolling under the approved age of the time),  where she was working  as a Sister on the children's ward at the beginning of the war until they were evacuated out of London. She then married Geoffrey Powell; they lived in north London and had one son, David Richard (born in 1942).

During the war she met Ralph Munday Denton-Barker (\p{Ralph_Munday_Denton-Barker}) and after divorcing her first husband, they married on 28 June, 1947.\cite{MarriageCertRalphDentonBarkerJoanNyriaPowell}

They moved to Pertenhall, Bedfordshire in 1948 and had one daughter, Julia (born in 1949).  In 1954 they moved to Dove Cottage, Great Witley, Worcestershire and Nyria had a very large garden, producing most of the family vegetables and fruit. She taught pottery to deaf children while living there.  In 1960 they moved to The Barn, Portloe, Cornwall and Nyria was very involved in community activities in the area, and also was a keen choir member.  They had a holiday house near Zennor, and their love of the area led them to buy Kerrow Farm, West Penwith, Cornwall in 1965 and she became a very active farmer for a few years as well as being engaged in the local arts community; she was also an accomplished water colourist and potter.

In 1970, they left Cornwall and  bought a smallholding called Casa Din-Ding, near Alayor, Menorca and she enjoyed  gardening in  a new climate and the challenge of living in a different country;  after a few years there, they moved to Mallorca and lived at Ca'an Amoros, near Pollensa where they had a large citrus orchard and a few cattle.  

In 1978 they sold most of their belongings and went to Australia by ship arriving in Fremantle on March 17th.  For the first year they lived at Lapkos Farm, Denmark, Western Australia, and then in 1979 they drove overland and went to live in Tasmania at Riverside Cottage, Upper Scamander. They had 7 acres of land and developed a large and productive garden. Nyria was instrumental in setting up the Neighbourhood House in St Helens (where some facilties are named after her)  and was very involved in the wider east coast community.  She and Ralph also enjoyed many camping trips around the island and also northern New South Wales where they spent time in various intentional communities. 

She lived alone at Riverside Cottage after Ralph's death in 1990, until having a cerebral aneurysm in December 2000 ; she then needed more care and lived at Medea Park, St Helens, but she still managed to maintain involvement and interest in her community activities.  She  died on 15 October 2004 in St Helens. Tasmania.
