\biohead{Jonathan Tong Barker}{}

He was born in 1883 \cite{JTBarkerBirth} in Liverpool, Lancashire, to Thomas Henry Barker (\p{Thomas_Henry_Barker}) and Mary Ellen Moulsdale (\p{Mary_Ellen_Moulsdale}). He had six siblings:  James Denton Barker (\p{James_Denton_Barker}), Charles Frederick Strangways Barker (\p{Charles_Frederick_Strangways_Barker}),  Reverend Thomas Percy Conyers Barker (\p{Thomas_Percy_Conyers_Barker}), Francis Darcy Mead Barker (\p{Francis_Darcy_Mead_Barker}), William Danby Holt Barker (\p{William_Danby_Holt_Barker}), and Henry Bertram Mitford Barker (\p{Henry_Bertram_Mitford_Barker}). 

He gained a PhD in chemistry and worked for a chemical company in the US for some years. He is recorded as arriving in New York, en route to Bay City, Michigan, on 3 December 1919, en route to Bay City, Michigan (chemist) and his next of kin is given as his mother. He returned to Liverpool on 29 November 1920 on the Baltic [JTBarkerTravel1]. 

He married Gladys Bythell Edwards in Holywell, Flinthshire, in Jan-Feb-Mar 1921. They had  no children.

 Then, on 3 July 1921, he is back in the USA on his way to Bay City having left Liverpool on 25 June, and this time he was travelling with his wife. They returned on 2 October 1921 travelling first class on the Caronia \cite{JTBarkerTravel2};  at the time,  they were living at Ormsby, West Kirby, Cheshire. 

He died on 4 February 1950 and was then living in Holywell, Flintshire, Wales and Probate was granted  on 24 April 1950 as follows:   
""Probate: Barker Jonathon Tong of Victoria Villa, Halkyn Street, Flint died 4 February 1950. Probate Bangor 24 April to Gladys Bythell Barker widow and Wilfred Bythell Edwards university professor. Effects (pounds) 1108.12s.7d""


