\biohead{Mary Gilmour}{c.~1890\cite{MaryGilmour1980}}

Mary Gilmour was born on 4 January 1843 in	Riccarton, Ayrshire, to \bioref{Boyd_Gilmour} and \bioref{Jean_Dunsmore}.\cite{MGilmourBirth}
She had six siblings: Jean Gilmour (1836--?), Joseph Gilmour (1840--?),
Marion Gilmour (1847--1928), Boyd Gilmour (1849--?), Allan Columbia Gilmour (1851--?) and John Gilmour (1854--1856).

On 9 December 1850, aged seven,  Mary  sailed on the ship The Pekin with her family, bound for Fort Vancouver, and the journey took 191 days. On 18 July 1851 they sailed to Fort Rupert, on Vancouver Island where her father took up a contract to develop a new coal mine.  She experienced living in very basic conditions at Fort Rupert, but when they moved south to Nanaimo, her mother refused to stay and took the children to Victoria, Vancouver Island. They returned to Scotland in 1854, and her mother Jean died in 1856.

In the 1861 Census, Mary is 18 years old, living in Old Hurlford, Kilmarnock, Ayrshire  with her father Boyd, sister Marian, and brothers Boyd and Allan Columbia. (Later that year Boyd remarried, to Elizabeth Howatson.)

Mary  married \bioref{Samuel_Maxwell_West_Croskery} on 13 August 1874 in Troon, Ayrshire (when she gave her age as 29, although she was in fact 31).\cite{SMWC-MG-marriage}  They had two daughters:  \bioref{Jeanie_Elenora_Dunsmuir_Croskery} and \bioref{Marian_Gilmour_Croskery}.
They lived in Troon until 1878, when they moved to Birkenhead, Cheshire.

Mary died in the first quarter of 1899 in Birkenhead at the age of 54. \cite{MGilmourDeath} 
