\biohead{Thomas Percy Conyers Barker}{}

 Thomas Percy Conyers Barker was born on 14 February 1879 in Liverpool, Lancashire to Thomas Henry Barker (\p{Thomas_Henry_Barker} and Mary Ellen Moulsdale (\p{Mary_Ellen_Moulsdale}).  He had six siblings, James Denton Barker (\p{James_Denton_Barker}), Charles Frederick Strangways Barker (\p{Charles_Frederick_Strangways_Barker}),  Francis Darcy Mead Barker (\p{Francis_Darcy_Mead_Barker}), William Danby Holt Barker (\p{William_Danby_Holt_Barker}),
Jonathan Tong Barker (\p{Jonathan_Tong_Barker}), and Henry Bertram Mitford Barker (\p{Henry_Bertram_Mitford_Barker}).
He was christened on 11 May 1879 at St.Brides, Liverpool, Lancashire  \cite{TPCBarkerBirth}. The family lived firstly at 10 Falkner Street, Liverpool  and then by 1881 at 44 Orrell Park, Walton on Hill \cite{TPCBarkerResidence}.

By 31 March 1901 he was working as a clerk for a Cotton Broker and lived at 36 Judges Lane, West Derby, Lancashire. \cite{TPCBarker1901}.  He then entered the Church and was ordained as a clergyman in 1906, and by 1911 he  was living in Northlew, Beaworthy, Devon  \cite{TPCBarker1911} and had married to Beatrice Maud Poole.

His entry in Crockfords reads as follows:

"Barker, Thomas Percy Conyers - St.Chad's Hall, Dur. B.A.1906 d (deacon)1906 p (Priest)1907 Dur. C. of St. Paul's, Jarrow, 1906-09; Northlew 1909-14; Bradninch 1914-17; Highweek 1918-19; Org. Sec. E.C.U. 1919-21; Commiss. Accra 1919-24; Dioc. Insp. of Schs. Dio. Chelmsf. 1926-46; V (Vicar) of Sampford Magna w Hempstead, Dio. Chelmsf. from 1921. (P Guild of All S.; 16a of G1 val 18l; Q.A.B.375l; Fees 4l; e.o.3l; Gross Inc. 401l, Net 338l and Ho (house); Pop. 794) Hempstead Vicarage, Saffron Walden, Essex." \cite{TPCBarkerCrockfords}

According to the above entry, he was a Commissiary for the Church in Accra, Ghana, from 1919-24.  A Commissiary was an officer exercising spiritual or ecclesiastical jurisdiction as the representative of the bishop in parts of his diocese.  He later became the Diocese Inspector of Schools for the Diocese of Chelmsford from 1926-1946.  

He died in Saffron Walden on 14 October 1948 \cite{TPCBarkerDeath} and the Probate notice read:

"Barker the Reverend Thomas Percy Conyers Barker of Great Sampford with Hempstead Vicarage, Saffron Walden, Essex died 14 October 1948 at the General Hospital, Saffron Walden. Probate Liverpool 11 August to Cyril George Edward Dingle solicitor, Effects (pounds)3075.16s.8d." 

