\biohead{Virginia Kathleen Denton Barker}{}

Virginia Kathleen Denton Barker was born on 7th September 1919 \cite{VKDBarkerManuscript} in Birkenhead to \bioref{James_Denton_Barker} and \bioref{Kathleen_Munday}.
She had two older brothers:  \bioref{Bertram_Mead_Denton_Barker} and \bioref{Ralph_Munday_Denton-Barker}.

She was educated at the Birkenhead High school for Girls (1924--37), and University College, London (1937--41). She graduated in 1941 in Anthropology, Economics and Psychology (II.i). From 1941 to 1945 she worked for the Wartime Social Survey (Ministry of Information) first as an interviewer and later in charge of the Survey of Sickness. From 1945--48 she worked with the Secretariat of the Royal Commission on Population. She was offered a place to read medicine at St. Bartholomew's Hospital in the first year that the Hospital admitted women as medical students. However, she did not take up this offer, instead marrying \bioref{Eugenia_Grebenik} on 28 December 1946\cite{VKDBarkerManuscript}. From 1948--60 she was engaged with domestic life and child rearing (Michael, Peter, and Catherine). From 1960--69 she worked as a part-time lecturer in Education at the Yorkshire College of Housecraft, which was to become Leeds Polytechnic and later, Leeds Metropolitan University. From 1973--84 she worked as the Psychiatric Social worker at Holloway Sanatorium, Virginia Water, Surrey. On retiring in 1978 she was active in forming the Runnymede Mental Health Association, which provided care for patients discharged from Holloway and for other patients who were living in the Community. She was also President of the RMHA. A new wing for day respite centre was named after her. \cite{VirginiaDocs}.

In later life, she and Eugene lived in Kidlington, Oxfordshire and she died in Wheatley, Oxfordshire  on 9th February 2006.
